Ants-Review: A Protocol For Open Anonymous Peer-Reviews\thanks{Supported by ETHTurin}

### 2020-06-05 paper-v1.tex
add bounty tech point

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\input{solidity-highlighting.tex}	% copy the file from this repo
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Ants-Review: A Protocol For Open Anonymous Peer-Reviews\thanks{Supported by ETHTurin}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304} \and
Nazzareno Massari\inst{2,3}\orcidID{0000-0002-6638-2174}}
%
\authorrunning{B. Trovò et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Sorbonne Université, Faculté des Sciences et Ingénierie, 75005 Paris, France \and
Neurospin research center, CEA/SAC/DSV/I2BM, 91191 Gif-sur-Yvette, France
\email{bianca.trovo@alumni.unitn.it}\\
\and
Polytechnic of Turin\\
\email{nazzareno@nazzarenomassari.com}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Peer-review is a necessary and essential quality control step for scientific publications. However, the process, which is very costly in terms of time investment, not only is not remunerated but it’s also not recognized by the academic community as a relevant scientific output for a researcher. Therefore, scientific dissemination is affected. Here, to solve this issue we propose a blockchain-based incentive protocol that rewards scientists also for their contributions to other scientists’ work and that builds up a reputational system. We designed a basic Bounty-like contract called AntsReview that allows any author to issue a call for peer-reviewing their scientific publication. If requirements are met, peer-reviews will be audited by an external editor and payed by the Issuer. To promote ethical behaviour the system will implement a quadratic funding on AntsReview.
\keywords{Blockchain  \and Peer-review \and Privacy \and Incentivization.}
\end{abstract}
%
%
\section{Introduction}

@@

\subsection{Implementation}
AntsReview is a destributed peer-review system which synthetizes successfull ideas from previous systems including The Bounty Network, ERC20, AZTEC Protocol, IPFS, Proof of Existence, DAO, ...
\newline The contribution of AntsReview is simply allowing the peer-review process, as a complex system, to emerge as a self-organised ecosystem of authors and peer-reviewers to enhance the complexity of a paper and its validation.
\newline AntsReview represent a new platform to issue peer-reviews and validate scientific papers and a new system for anonymous and open contributions with an incentivization mechanism to reach an ideal state of equilibrium and create value.
\newline The AntsReview Protocol is divided into stack of sub-protocols responsible for different functionality:

\begin{enumerate}}
  \item \textbf{Bounty} - manage access management and the basic system.
  \item \textbf{Token Economics} - manage system incentivization mechanism integrating ideas from DeFi and Quadratic Funding.
  \item \textbf{Privacy} - mantains the anonymity of the system via AZTEC Protocol.
  \item \textbf{DAO} - manage the governance of the system via DemocracyDAO.
\end{enumerate}

\subsubsection{Bounty}

\begin{lstlisting}[language=Solidity]
pragma solidity 0.4.16;

contract TestContract {

	string private myString = "foo";

	function getString() constant returns (string) {
	    return myString;
	}

	function setString (string _string) {
	    myString = _string;
	}
}
\end{lstlisting}

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\graphicspath{ {./img/} }

\input{solidity-highlighting.tex}	% copy the file from this repo
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Ants-Review: A Protocol For Open Anonymous Peer-Reviews\thanks{Supported by ETHTurin}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304} \and
Nazzareno Massari\inst{2,3}\orcidID{0000-0002-6638-2174}}
%
\authorrunning{B. Trovò et N. Massari}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Sorbonne Université, Faculté des Sciences et Ingénierie, 75005 Paris, France \and
Neurospin research center, CEA/SAC/DSV/I2BM, 91191 Gif-sur-Yvette, France
\email{bianca.trovo@alumni.unitn.it}\\
\and
Polytechnic of Turin\\
\email{nazzareno@nazzarenomassari.com}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Peer-review is a necessary and essential quality control step for scientific publications. However, the process, which is very costly in terms of time investment, not only is not remunerated but it’s also not recognized by the academic community as a relevant scientific output for a researcher. Therefore, scientific dissemination is affected. Here, to solve this issue we propose a blockchain-based incentive protocol that rewards scientists also for their contributions to other scientists’ work and that builds up a reputational system. We designed a basic Bounty-like contract called AntsReview that allows any author to issue a call for peer-reviewing their scientific publication. If requirements are met, peer-reviews will be audited by an external editor and payed by the Issuer. To promote ethical behaviour the system will implement a quadratic funding on AntsReview.
\keywords{Blockchain  \and Peer-review \and Privacy \and Incentivization.}
\end{abstract}
%
%
\section{Introduction}

@@

\subsection{Implementation}
AntsReview is a destributed peer-review system which synthetizes successfull ideas from previous systems including The Bounty Network[ref], ERC20[ref], AZTEC Protocol[ref], IPFS[ref], Proof of Existence[ref], ...
\newline The contribution of AntsReview is simply allowing the peer-review process, as a complex system, to emerge as a self-organised ecosystem of authors and peer-reviewers to enhance the complexity of a paper and its validation.
\newline AntsReview represent a new platform to issue peer-reviews and validate scientific papers and a new system for anonymous and open contributions with an incentivization mechanism to reach an ideal state of equilibrium and create value.
\newline The AntsReview Protocol is divided into stack of sub-protocols responsible for different functionality:

\includegraphics[scale=0.28]{AntsReview}

\begin{enumerate}
  \item \textbf{Bounty} - manage access management and the basic system.
  \item \textbf{Token Economics} - manage system incentivization mechanism integrating ideas from DeFi and Quadratic Funding.
  \item \textbf{Privacy} - mantains the anonymity of the system via AZTEC Protocol.
\end{enumerate}

\subsubsection{Bounty}
AntsReview is the core of the smart contracts deployed on Ethereum Rinkeby's Testnet as shown in the flow-chart[img].
\newline It implements a Bounty-like system where an issuer (author) is asked a serious of actions, to ensure transparency and robustness, regarding the AntReview that he's creating:
\begin{itemize}
  \item to upload the file containing the requirements of the peer-review and the paper into IPFS.
  \item to speficy a deadline in the form of a unix timestamp after wich the fulfillment will no longer be accepted.
  \item to send the amount of ether for the reward.
\end{itemize}

AntsReviewRoles, to ensure integrity of the system, implements an access management, leveraging on AccessControl.sol by OpenZeppelin Library, through the creation of the Roles Issuer and Peer-Reviewer[code].

\begin{lstlisting}[language=Solidity]

pragma solidity 0.6.8;

import "@openzeppelin/contracts/access/AccessControl.sol";

contract AntsReviewRoles is AccessControl {

/// Roles
bytes32 public constant ISSUER_ROLE = keccak256("ISSUER_ROLE");
bytes32 public constant PEER_REVIEWER_ROLE = keccak256("PEER_REVIEWER_ROLE");

}
\end{lstlisting}

In this way, only the Issuer (author) can create a new AntReview.
\newline Once created, an AntReview is available to be fulfilled by Peer-Reviewers, uploading the peer-review on IPFS before the deadline.
\newline The AntReview after being validated is then accepted by the Issuer and paid equally between Peer-Reviewers.
\newline Also, the Issuer can cancel the AntReview at any time and withdraw the amount of ether staked.
One of the key aspects of the protocol is the concept of Proof of Existence, introduced by Stuart Haber & W. Scott Stornetta with the paper "How to time-stamp a digital document".
\newline As the pioneer of blockchain an cited by Bitcoin whitepaper, they were in a mission to solve the problem of immutability of digital records that became reality with Bitcoin and Blockchain.
\newline In Ethereum the concept of immutablity is achieved via the blockchain and proof of work consesus algorithm by a chain of timestamped block hashes that are secured by miners competing computations.
\newline AntsReview is evaluating the advantages of storing the hashes of the peer-reviews into a Merkle Tree to achieve immutability.
